\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-07-31 write_up/mixfishsim_ecolmod.tex
Updated figures

We parametrised the simulation model for four populations with different
demographics; growth rates, natural mortality and recruitment functions (Table
\ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were defined to be unique to
each population resulting in differently weekly distribution patterns (Figures
\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations was assumed
to have two defined spawning areas that result in the populations moving
towards these areas in pre-defined weeks (Figure \ref{S-fig:2}) with
population-specific movement rates (Table \ref{tab:1}). In such a
configuration, the individual habitat preferences and thermal tolerances result
in different spatial habitat use for each population (Figure \ref{S-fig:9}) and
consequently different seasonal exploitation patterns (Fishing mortality in
Figure \ref{S-fig:10}).

@@

It can be seen from a single vessels movements during a trip that the vessel
exploits four different fishing grounds, three of them multiple times (Figure
\ref{S-fig:11}), while across several trips fishing grounds that are further
apart are fished (Figure \ref{S-fig:12}). These different locations relate to
areas where the highest revenue were experienced, as shown by
\added[id=PD]{Figure} \ref{S-fig:13}, where several trips for the vessel
overlaid on the revenue field, i.e. 
$$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$

@@

A regression tree (using the R package REEMtree \citep{Sela2012}) highlights
that the factor most contributing to differences in fishing mortality before
and after the closure was the population (72 \% showing that the closures were
effective for population 3), followed by data resolution (21 \%), data type (7
\%) with the least important factor the timescale ($<$ 1 \%). In general the
finer the spatial resolution of the data used the greater reduction in fishing
mortality for population 3 after the closures (Figure \ref{fig:4}). The notable
outliers are the commercial data at the coarsest spatial resolution (20 x 20)
at a yearly and weekly timescale, where closures were nearly as effective as
the fine-scale resolution. In this case the closures were sufficiently large to
protect a core are of the habitat for the population, but this was achieved in
a fairly crude manner by closing a large area - including area where the
species was not found (Figure \ref{S-fig:17}) that may have consequences in
terms of restricting the fishery in a much larger area than necessary. \\

@@

From our simulations spatial disaggregation was more important than the
temporal disaggregation of the commercial data. This reflects the fact that
there was greater spatial heterogeneity over the spatial domain than
experienced in individual locations over the course of the year (Figure
\ref{S-fig:9}). This indicates that fixed closures, at the right resolution,
when based on commercially derived data have the potential to reduced fishing
mortality. The likely cost of poor spatial and temporal resolution is
associated with reduced effectiveness and potentially closing fishing
opportunities for other fisheries. \\

@@

@@

>>>>

We parametrised the simulation model for four populations with different
demographics; growth rates, natural mortality and recruitment functions (Table
\ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were defined to be unique to
each population resulting in differently weekly distribution patterns (Figures
\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations was assumed
to have two defined spawning areas that result in the populations moving
towards these areas in pre-defined weeks (Figure \ref{S-fig:2}) with
population-specific movement rates (Table \ref{tab:1}). In such a
configuration, the individual habitat preferences and thermal tolerances result
in different spatial habitat use for each population (Figure \ref{fig:9}) and
consequently different seasonal exploitation patterns (Fishing mortality in
Figure \ref{fig:10}).

@@

It can be seen from a single vessels movements during a trip that the vessel
exploits four different fishing grounds, three of them multiple times (Figure
\ref{S-fig:11}), while across several trips fishing grounds that are further
apart are fished (Figure \ref{S-fig:12}). These different locations relate to
areas where the highest revenue were experienced, as shown by
\added[id=PD]{Figure} \ref{fig:13}, where several trips for the vessel
overlaid on the revenue field, i.e. 
$$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$

@@

A regression tree (using the R package REEMtree \citep{Sela2012}) highlights
that the factor most contributing to differences in fishing mortality before
and after the closure was the population (72 \% showing that the closures were
effective for population 3), followed by data resolution (21 \%), data type (7
\%) with the least important factor the timescale ($<$ 1 \%). In general the
finer the spatial resolution of the data used the greater reduction in fishing
mortality for population 3 after the closures (Figure \ref{fig:4}). The notable
outliers are the commercial data at the coarsest spatial resolution (20 x 20)
at a yearly and weekly timescale, where closures were nearly as effective as
the fine-scale resolution. In this case the closures were sufficiently large to
protect a core are of the habitat for the population, but this was achieved in
a fairly crude manner by closing a large area - including area where the
species was not found (Figure \ref{fig:17}) that may have consequences in
terms of restricting the fishery in a much larger area than necessary. \\

@@

From our simulations spatial disaggregation was more important than the
temporal disaggregation of the commercial data. This reflects the fact that
there was greater spatial heterogeneity over the spatial domain than
experienced in individual locations over the course of the year (Figure
\ref{fig:9}). This indicates that fixed closures, at the right resolution,
when based on commercially derived data have the potential to reduced fishing
mortality. The likely cost of poor spatial and temporal resolution is
associated with reduced effectiveness and potentially closing fishing
opportunities for other fisheries. \\

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/pop_dist}
	\caption{Simulated spatial dynamics - the four populations abundance
		(log+1) at four time steps.
		}
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		showing weekly and seasonal patterns in exploitation.
		Individual years and the light grey lines, the mean of all
		years the thick black line}
	\label{fig:10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/vessel_move_value}
	\caption{movement of a fleet over a single trip reference overlaid on the
		value field (i.e. sum of the population abundance x catchability x value}
	\label{fig:13}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{Closure fishing locations based on annual closures with a
		coarse spatial resolution. Closure location can be seen in red
	in relation to a) before the closure fishing locations, b) after the
	closure fishing locations, c) species 3 habitat distribution}
	\label{fig:17}
\end{figure}
